---
title: "ARGO"
author: "Nicholas Baetge"
date: "2/6/2020"
output: html_document
---

# Intro

This document highlights how MLDs were calculated from the ARGO floats deployed on the NAAMES cruises. 

- Input data, which were the level 2 processed data, were pulled from the [NAAMES data page](https://naames.larc.nasa.gov/data2018.html)
- MLDs were calculated using the N^2^ buoyancy frequency and are defined as the depth below 5 m at which N^2^ > |stdev(N^2^)|

```{r include=FALSE}
library(tidyverse)
library(knitr)
library(data.table) 
library(zoo) 
library(oce)  
library(scales)
#for mapping
library(marmap)
library(ggrepel)
library(ocedata)
library(ggmap)
#for odv type plots
library(lubridate)
library(reshape2)
library(MBA)
library(mgcv)
#colors
library(RColorBrewer)


custom_theme <- function () {
  theme_test(base_size=30) %+replace%
    theme(legend.position="top",
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA)) 
}
```

# Import and Wrangle Data

```{r warning = FALSE, message = FALSE}
#load each float dataset
lovbio014b <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/lovbio014b_profiles.csv") %>%  
  mutate(float = "lovbio014b") %>% select(float, id, datetime:s, chla_adj) %>%
  rename(chla = chla_adj)
lovbio030b <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/lovbio030b_profiles.csv") %>%  
  mutate(float = "lovbio030b") %>% select(float, id, datetime:s, chla_adj) %>%
  rename(chla = chla_adj)
lovbio032b <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/lovbio032b_profiles.csv") %>%  
  mutate(float = "lovbio032b") %>% select(float, id, datetime:s, chla_adj) %>%
  rename(chla = chla_adj)
metbio003d <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/metbio003d_profiles.csv") %>%  
  mutate(float = "metbio003d") %>% select(float, id, datetime:s, chla_adj) %>%
  rename(chla = chla_adj)
metbio010d <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/metbio010d_profiles.csv") %>%  
  mutate(float = "metbio010d") %>% select(float, id, datetime:s, chla_adj) %>%
  rename(chla = chla_adj)
#this dataset contained NANs which are problematic for the potential temperature and n2 calculations. thus, they are removed here. 
metbio010d <- metbio010d[complete.cases(metbio010d),] 
n0572 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0572_profiles.csv") %>%  
  mutate(float = "n0572") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0573 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0573_profiles.csv") %>%  
  mutate(float = "n0573") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0574 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0574_profiles.csv") %>%  
  mutate(float = "n0574") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0646 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0646_profiles.csv") %>%  
  mutate(float = "n0646") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0647 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0647_profiles.csv") %>%  
  mutate(float = "n0647") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0648 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0648_profiles.csv") %>%  
  mutate(float = "n0648") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0846 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0846_profiles.csv") %>%  
  mutate(float = "n0846") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0847 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0847_profiles.csv") %>%  
  mutate(float = "n0847") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0848 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0848_profiles.csv") %>%  
  mutate(float = "n0848") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0849 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0849_profiles.csv") %>%  
  mutate(float = "n0849") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0850 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0850_profiles.csv") %>%  
  mutate(float = "n0850") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0851 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0851_profiles.csv") %>%  
  mutate(float = "n0851") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)
n0852 <- read_csv("~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Input/Argo/n0852_profiles.csv") %>%  
  mutate(float = "n0852") %>% select(float, id, datetime:s, o2_c, chla_adj) %>%
  rename(chla = chla_adj)

#combine all the float data
#this first set of floats don't have O2 data
collab_floats.df <- rbind(lovbio014b, lovbio030b, lovbio032b, metbio003d, metbio010d) %>% 
  rename(profile = id) 

naames_floats.df <- rbind(n0572, n0573, n0574, n0647, n0648, n0846, n0847, n0848, n0849, n0850, n0851, n0852) %>% 
  rename(profile = id)

all_floats.df <- naames_floats.df %>% 
  select(-o2_c) %>% 
  rbind(., collab_floats.df) %>% 
  drop_na() 

```

# Calculations

## MLDs

```{r warning = FALSE, message = FALSE}
float_mld.df  <- all_floats.df %>% 
  group_by(float, profile, datetime) %>% 
  mutate(sigmaT = swSigmaTheta(s, temperature = t, pressure = p, referencePressure = 0), 
         N2 = swN2(pressure = p, sigmaTheta = sigmaT),
         Date = as.Date(datetime, "%m/%d/%y"), 
         Month = month(Date)) %>% 
  #include only depths below 5 m and where  N2 is > abs(stdev(N2))
  filter(p > 5 & N2 > abs(sd(N2))) %>%  
  filter(p == min(p)) %>% #report the shallowest depth at which the above condition is met
  rename(MLD = p) %>% 
  ungroup() %>% 
  select(float, profile, datetime, Date, Month, lat:MLD) %>% 
  #set longitudinal and latitudinal bounds based on the extent of the NAAMES region
  filter(between(lon, -47, -38),
         between(lat, 39,57)) %>% 
  mutate(bin = round(lat)) %>% 
  arrange(bin, Date) %>%
  select(float:datetime, lat, lon, bin, MLD) %>% 
  group_by(bin) %>% 
  add_tally() %>% 
  rename(nperbin = n) %>% 
  ungroup()

mld_winter <- float_mld.df %>% 
  select(float, profile, datetime, bin) %>%
  mutate(month = month(datetime)) %>% 
  filter(month %in% c(11,12,1,2,3,4)) %>% 
  select(float, profile, month, bin) %>% 
  group_by(bin) %>% 
  add_tally() %>% 
  rename(nperwinter = n) %>% 
  select(bin, nperwinter) %>% 
  distinct() %>% 
  ungroup()

float_mld.df <- left_join(float_mld.df, mld_winter)
  
```

## Chl

```{r}
float_chl.df <- all_floats.df %>% 
  #set longitudinal and latitudinal bounds based on the extent of the NAAMES region
  filter(between(lon, -47, -38),
         between(lat, 39,57)) %>% 
  group_by(float, profile, datetime) %>% 
  select(float:t, chla) %>% 
  #correct the chlorophyll data for each profile by subtracting the min from each observation
  mutate(min_fl = min(chla),
         cor_fl = chla - min_fl) %>% 
  select(float:t, cor_fl)
```

## Max MLD

```{r message = FALSE}
float_combined.df <- left_join(float_mld.df, float_chl.df) %>% 
  mutate(decimaldate = decimal_date(datetime)) %>% 
  ungroup() %>%
  select(float, profile, datetime, decimaldate, lat, lon, bin, MLD, nperbin, nperwinter, p, t, cor_fl) %>% 
  drop_na() %>% 
  arrange(bin, decimaldate) 

max_mld.df <- float_combined.df %>% 
  arrange(bin, datetime) %>% 
  group_by(bin) %>% 
  select(float:nperwinter) %>% 
  distinct() %>% 
  mutate(max_mld = max(MLD)) %>% 
  filter(MLD == max_mld) %>% 
  select(-MLD) %>% 
  distinct(.) %>% 
  mutate(date = date_decimal(decimaldate),
         mon = month(date, label=TRUE, abbr=TRUE),
         year = year(date)) %>% 
  arrange(bin) %>% 
  select(bin, nperbin, nperwinter, max_mld, float, profile, mon, year, lat, lon )

saveRDS(max_mld.df, "~/Google Drive File Stream/Shared drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Output/max_mld.rds")

```

```{r echo = FALSE, results = 'asis'}
kable(max_mld.df, caption = "ARGO Maximum Mixed Layers")
```

# ODV style plot 

## Interpolate temperature data

```{r}
#subset the temperature and the mld data separately

t.df <- float_combined.df %>% 
  #deepest mixed layer observed from floats in NAAMES region was 508
  filter(between(p, 0, 550)) %>% 
  select(bin, decimaldate, p, t) %>% 
  arrange(decimaldate, bin) %>% 
  group_by(bin) 

mld.df <- float_combined.df %>% 
  filter(between(p, 0, 550)) %>% 
  select(bin, decimaldate, MLD) %>% 
  arrange(decimaldate, bin) %>% 
  group_by(bin) 

#split chl data into a list by latitudinal bin
t.list <- split(t.df, t.df$bin)

#create function to interpolate chl
interp.func <- function(casper) {
  dog <- casper %>% 
    ungroup() %>% 
    #the interpolation requires that the dataframe be comprised of only 3 columns (x, y, z)
    select(-bin) 
  mba <- mba.surf(dog, no.X = 300, no.Y = 300, extend = T)
  dimnames(mba$xyz.est$z) <- list(mba$xyz.est$x, mba$xyz.est$y)
  mba <- melt(mba$xyz.est$z, varnames = c('decimaldate', 'p'), value.name = 't') %>% 
    filter(p > 0)
}

#apply the interpolation function to the list
interpolated_t.list <- lapply(t.list, interp.func)

#convert the list into a df for plotting
interpolated_t.df <- data.frame(rbindlist(interpolated_t.list, idcol = T)) %>% 
  mutate(.id = as.numeric(.id)) %>% 
 rename(bin = .id) %>% 
  arrange(decimaldate, bin) %>% 
  group_by(bin) 

```

## Plot

```{r fig.align="center", fig.height=10, fig.width=16, echo = FALSE, message=FALSE, warning=FALSE}

###change odv.bin to plot different latitudinal bins
#lat range is 39-57
odv.bin <- 52


t.odv <- t.df %>% filter(bin == odv.bin)

interp_t.odv <- interpolated_t.df %>% filter(bin == odv.bin)

mld.odv <- mld.df %>% filter(bin == odv.bin) %>% distinct(.)
mld_spline.odv <- as_data_frame(spline(mld.odv$decimaldate, mld.odv$MLD))

odv.plot <-  interp_t.odv %>% 
  ggplot(aes(x = decimaldate, y = p)) + 
  geom_raster(aes(fill = t)) +
    geom_point(data = t.odv, aes(x = decimaldate, y = p, colour = t), colour = "Black", alpha = 0.3, size = 0.25, shape = 3) +
  geom_line(data = mld.odv, aes(x = decimaldate, y = MLD), colour = "White", linetype = 2, size = 1 ) +
    geom_point(data = mld.odv, aes(x = decimaldate, y = MLD), colour = "White", shape = 19, size = 3, alpha = 0.8) +
    #option = "plasma" or "cividis" look good here
    scale_fill_viridis_c(option = "viridis", direction = 1) + 
    scale_y_reverse(breaks = pretty_breaks()) +
    scale_x_continuous(breaks = pretty_breaks()) +
    labs(y = expression(italic("Depth, m")), x = expression(italic("Decimal Date")), fill = expression(italic(paste("Temperature, ˚C")))) +
    guides(fill = guide_colourbar(barheight = 2, barwidth = 20)) +
    custom_theme() 

odv.plot
```

```{r include = FALSE}
#saveRDS(odv.plot, file = "~/Google Drive File Stream/Shared Drives/NAAMES_Carlson/DATA/FINAL/MANUSCRIPT_DATA/Export_MS/Figures/ARGO_52N.rds")

#ggsave("Figure1b.jpg", odv.plot, device = "jpg",  width = 16, height= 10, path="~/Desktop/Export_MS/Submission2/") 
```

