---
title: "Export_MS"
author: "Nicholas Baetge"
date: "1/30/2020"
output: github_document
---

# Intro

This document is primarily used to plot data generated from the analyses conducted for the NAAMES DOC export manuscript. 

```{r include=FALSE}
library(tidyverse) 
library(rmarkdown)
library(knitr)
library(data.table) #these two libraries allow for data manipulation operations like join dataframes
library(zoo) #this package allows for the interpolation function
library(oce) #allows for processing and visualization of oceanographic data. Here, it is used for running integrations.
library(lattice)
library(scales)
library(gridExtra)
library(grid)
#for time
library(lubridate)
#### bar plot
library(broom)
#stat tests
library(lmtest)
library(lmodel2)
#image conversion
library(magick)
library(pdftools)
library(jpeg)
#rmarkdown tables
library(stargazer)
library(pander)
#for mapping
library(marmap)
library(ggrepel)
library(ocedata)
library(ggmap)

```


```{r include = FALSE}
custom_theme <- function() {
  theme_test(base_size = 40) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA)) 
}

custom_theme2 <- function() {
  theme_test(base_size = 30) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA)) 
}


custom.colors <- c("AT39" = "#377EB8", "AT34" = "#4DAF4A", "AT38" = "#E41A1C", "AT32" = "#FF7F00", "Temperate" = "#A6CEE3", "Subpolar" = "#377EB8", "Subtropical" = "#FB9A99", "GS/Sargasso" = "#E41A1C", "Early Spring" = "#377EB8", "Late Spring" = "#4DAF4A","Early Autumn" = "#E41A1C", "Summer" = "#E41A1C", "Late Autumn" = "#FF7F00", "Gv2_2019" = "#377EB8", "WOA18_MN" = "#4DAF4A", "WOA18_AN" = "#E41A1C")

levels = c("GS/Sargasso", "Subtropical", "Temperate", "Subpolar",  "AT39-6", "AT34", "AT38", "AT32","South", "North", "Early Spring", "Late Spring","Early Autumn",  "Summer", "Late Autumn", "Gv2_2019", "WOA18_MN", "WOA18_AN","Nov", "Nov sd", "Dec", "Dec sd", "Jan", "Jan sd", "Feb", "Feb sd", "Mar", "Mar sd", "Apr", "Apr sd",  "Cruise", "ARGO")

bar.colors <- c("100 m" = "white", "CM" = "#4DAF4A",  "PAM" = "#377EB8")

```

# Import and Wrangle Data

```{r message = F}

processed_bf <- read_rds("~/naames_export_ms/Output/processed_bf.2.2020.rds")

processed_export <- read_rds("~/naames_export_ms/Output/processed_export_n2_n3.rds") 

processed_export$Season <- factor(processed_export$Season, levels = levels)

processed_export.spr <- processed_export %>% 
  filter(Season %in% c("Late Spring")) 
 

processed_export.aut <- processed_export %>% 
  filter(Season %in% c("Early Autumn"))  
  

```

## Data for Regressions

We'll use station/day averages for any model regressions we conduct. 

```{r}
regression.means <- processed_export %>% 
  filter(!Cruise == "Early Spring") %>% 
  select(Cruise:Subregion, NCP_mol_100, NCP_mol_cm, NCP_mol_phy, int_delta_DOC_100, int_delta_DOC_100_maxmld,int_delta_DOC_phy, int_delta_DOC_cm, doc_ncp_100:si_ncp_100, int_Pro_cm_vol:int_Nano_phy_vol) %>%
  distinct() %>% 
  group_by(Cruise, Station) %>% 
  mutate_at(vars(NCP_mol_100:int_Nano_phy_vol), mean, na.rm = T) %>% 
  distinct() %>% 
  ungroup()
regression.means[ is.na(regression.means) ] <- NA


regression.means.spr <- regression.means %>% 
  filter(Season == "Late Spring")

regression.means.aut <- regression.means %>% 
  filter(Season == "Early Autumn")
```

# Tables

```{r include = FALSE}
table.integrations <-  processed_export %>% 
  select(Season, Station, ave_lat, ave_lon,  NCP_mol_100, NCP_mol_cm, NCP_mol_phy, int_delta_DOC_100, int_delta_DOC_cm, int_delta_DOC_phy, doc_ncp_100, doc_ncp_cm, doc_ncp_phy) %>% 
 arrange(Season, ave_lat) %>% 
  distinct() %>% 
  mutate_at(vars(NCP_mol_100:doc_ncp_phy),round,2) %>% 
  rename(NCP_100 = NCP_mol_100,
         DOC_NCP_100 = doc_ncp_100,
         Delta_DOC_100 = int_delta_DOC_100,
         NCP_CM = NCP_mol_cm,
         DOC_NCP_CM = doc_ncp_cm,
         Delta_DOC_CM = int_delta_DOC_cm,
         NCP_PM = NCP_mol_phy,
         DOC_NCP_PM = doc_ncp_phy,
         Delta_DOC_PM = int_delta_DOC_phy,
        )


table.spr <-  processed_export.spr %>% 
  select(Station, ave_lat, ave_lon, degree_bin, Subregion, ave_date,  Max_MLD, ave_chlmax:sd_pmax, redis_N_vol, redis_DOC_vol, redis_Si_vol, int_delta_N_100, NCP_mol_100, doc_ncp_100, int_delta_DOC_100, int_delta_Si_100, si_n_100, si_ncp_100) %>% 
 arrange(degree_bin) %>% 
  distinct() %>% 
  mutate_at(vars(redis_N_vol:si_ncp_100),round,2) %>% 
  rename(Bin = degree_bin, 
         Mixed_N = redis_N_vol,
         Mixed_DOC = redis_DOC_vol,
         Mixed_Si = redis_Si_vol,
         Delta_N = int_delta_N_100,
         NCP = NCP_mol_100,
         DOC_NCP = doc_ncp_100,
         Delta_DOC = int_delta_DOC_100,
         Delta_Si = int_delta_Si_100,
         Si_N = si_n_100,
         Si_NCP = si_ncp_100)
  

table.aut <-  processed_export.aut %>% 
  select(Station, ave_lat, ave_lon, degree_bin, Subregion, ave_date,  Max_MLD, ave_chlmax:sd_pmax, redis_N_vol, redis_DOC_vol, redis_Si_vol, int_delta_N_100, NCP_mol_100, doc_ncp_100, int_delta_DOC_100, int_delta_DOC_100_maxmld, int_delta_Si_100, si_n_100, si_ncp_100) %>% 
  arrange(degree_bin) %>% 
  distinct() %>% 
  mutate_at(vars(redis_N_vol:si_ncp_100),round,2) %>% 
  rename(Bin = degree_bin, 
         Mixed_N = redis_N_vol,
         Mixed_DOC = redis_DOC_vol,
         Mixed_Si = redis_Si_vol,
         Delta_N = int_delta_N_100,
         NCP = NCP_mol_100,
         DOC_NCP = doc_ncp_100,
         Delta_DOC = int_delta_DOC_100,
         Delta_DOC_mz = int_delta_DOC_100_maxmld,
         Delta_Si = int_delta_Si_100,
         Si_N = si_n_100,
         Si_NCP = si_ncp_100)

```
## Table 1. ARGO Observations

See ARGO.Rmd document

## Table 2. Early Autumn

```{r echo = FALSE, results = 'asis'}
kable(table.aut, caption = "Early Autumn")
```


## Table 3. Late Spring
```{r echo = FALSE, results = 'asis'}
kable(table.spr, caption = "Late Spring")
```


## Supplemental Table 1. Integrations

```{r echo = FALSE, results = 'asis'}
kable(table.integrations, caption = "Integration Comparisons")
```


## Supplemental Table 2. ∆DOC:NCP v Phytoplankton

```{r message = FALSE}
si_t2_data <- regression.means.aut %>% 
  select(Subregion, doc_ncp_cm, doc_ncp_phy, int_Syn_cm_vol, int_Syn_phy_vol, int_Pico_cm_vol, int_Pico_phy_vol, int_Nano_cm_vol, int_Nano_phy_vol  ) %>% 
  distinct()
lmodel2(doc_ncp_cm ~ int_Syn_cm_vol, data = si_t2_data, nperm = 99)
```

```{r message = FALSE}
lmodel2(doc_ncp_phy ~ int_Syn_phy_vol, data = si_t2_data, nperm = 99) 
```


```{r message = FALSE}
lmodel2(doc_ncp_cm ~ int_Pico_cm_vol, data = si_t2_data, nperm = 99)
```


```{r message = FALSE}
lmodel2(doc_ncp_phy ~ int_Pico_phy_vol, data = si_t2_data, nperm = 99)

```

```{r message = FALSE}
lmodel2(doc_ncp_cm ~ int_Nano_cm_vol, data = si_t2_data, nperm = 99)
```


```{r message = FALSE}
lmodel2(doc_ncp_phy ~ int_Nano_phy_vol, data = si_t2_data, nperm = 99)
```


# Figure 1. Cruise Map & Floats

See Cruise_Map.Rmd and ARGO.Rmd  documents

# Figure 2. MLD Comparison

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 12, fig.align = "center", warning = FALSE}
mlds <- processed_bf %>% 
  select(Season, Station, CampCN, degree_bin, Latitude, Max_MLD, Z_MLD) %>%
  group_by(Season, Station) %>% 
  mutate(mean_mld = mean(Z_MLD),
         sd_mld = sd(Z_MLD),
         ave_lat = mean(Latitude)) %>% 
  ungroup() %>% 
  select(Season, Station, degree_bin, ave_lat, Max_MLD, mean_mld, sd_mld) %>% 
  distinct() 

naames_mld <- mlds %>% 
  select(-Max_MLD, -degree_bin) %>% 
  distinct()

argo_mld <- mlds %>% 
  select(Season, degree_bin, Max_MLD) %>% 
  distinct()

naames_mld.plot <- naames_mld %>% 
  ggplot() +
  geom_errorbar(aes(x = ave_lat, ymin = mean_mld - sd_mld, ymax = mean_mld + sd_mld)) +
  geom_point(aes(x = ave_lat, y = mean_mld, fill = Season), size = 6, shape = 21, color = "black", stroke = 1, alpha = 0.7) +
  geom_point(data = argo_mld, aes(x = degree_bin, y = Max_MLD), size = 8, shape = 22, color = "black", fill = "yellow", stroke = 1, alpha = 0.7) +
  scale_y_reverse(expand = c(0,0)) +
  scale_colour_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  custom_theme2() +
  labs(x = expression(italic("Latitudinal Bin, ˚N")), y = expression(italic("Maximum Mixed Layer, m")))

naames_mld.plot
```
```{r include = FALSE}
# ggsave("f2.jpg", naames_mld.plot, device = "jpg",  width = 12, height = 8, path = "~/Desktop/Export_MS/Submission2/") 
```


# Figure 3. Early Autumn Profiles 


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 14, fig.align = "center", warning = FALSE}

profiles.df <- processed_export.aut %>% 
  filter(Target_Z %in% c(0,5,10,25,50,75,100,150,200,300,400,500),
         Station == 5) 

n <-  profiles.df %>% 
  ggplot(aes(x = Target_Z, y = ave_N)) +
   geom_segment(aes( x = Max_MLD, xend = Max_MLD, y = min(ave_N), yend = max(ave_N), group = Station ), colour = "#377EB8", linetype = 3, size = 2 ) +
  geom_segment(aes(y = redis_N_vol, yend = redis_N_vol, x = 0, xend = Max_MLD, group = Station ), colour = "black", linetype = 2, size = 1.5, alpha = 0.7 ) +
  geom_segment(aes(x = 100, xend = 100, y = min(ave_N), yend = max(ave_N), group = Station), colour = "black", linetype = 3, size = 2) +
  geom_line(aes(colour = Season), size = 0.7) +
  geom_point(aes(fill = Season), size = 6, shape = 21, color = "black", stroke = 1, alpha = 0.7) + 
  labs(x = expression(paste(italic("Depth, m"))), y = expression(italic(paste("NO"[3],", µmol N L"^"-1"))), colour = "") +
   scale_x_reverse(breaks = pretty_breaks(), expand = c(0,0)) +
  coord_flip() +
  scale_y_continuous(expand = c(0,0)) +
  scale_colour_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  guides(colour = F) +
  guides(fill = F) +
  custom_theme2() +
  annotate( geom = "text", label = expression(bolditalic(paste("Z"["Max MLD"]))), y = 5, x = 350, size = 12, color = "#377EB8") +
  annotate( geom = "text", label = expression(bold(paste("Mixed Profile"))), y = 7, x = 200, size = 10) +
   geom_segment(aes(x = 215, xend = 215, y = 5, yend = 12),
     lineend = "round", linejoin = "mitre",
     size = 2, arrow = arrow(length = unit(0.3, "inches"))
  ) +
   annotate( geom = "text", label = expression(bolditalic(paste("∆NO"[3]))), y = 7, x = 25, size = 12) 
  

doc <-  profiles.df %>% 
  ggplot(aes(x = Target_Z, y = ave_DOC)) +
  geom_segment(aes( x = Max_MLD, xend = Max_MLD, y = min(ave_DOC), yend = max(ave_DOC), group = Station ), colour = "#377EB8", linetype = 3, size = 2 ) +
  geom_segment(aes(y = redis_DOC_vol, yend = redis_DOC_vol, x = 0, xend = Max_MLD, group = Station ), colour = "black", linetype = 2, size = 1.5, alpha = 0.7 ) +
  geom_segment(aes(x = 100, xend = 100, y = min(ave_DOC), yend = max(ave_DOC), group = Station), colour = "black", linetype = 3, size = 2) +
  geom_line(aes(colour = Season), size = 0.7) +
  geom_point(aes(fill = Season), size = 6, shape = 21, color = "black", stroke = 1, alpha = 0.7) + 
  labs(x = expression(paste("")), y = expression(italic(paste("DOC, µmol C L"^"-1"))), colour = "") +
  scale_x_reverse(breaks = pretty_breaks(), expand = c(0,0)) +
  coord_flip() +
  scale_y_continuous(expand = c(0,0)) +
  scale_colour_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  guides(colour = F) +
  guides(fill = F) +
  custom_theme2() +
   annotate( geom = "text", label = expression(bold(paste("Export"))), y = 61, x = 200, size = 10, color = "#552583") +
   geom_segment(aes(x = 215, xend = 215, y = 64, yend = 55.6),
     lineend = "round", linejoin = "mitre",
     size = 2, arrow = arrow(length = unit(0.3, "inches"))) +
   annotate( geom = "text", label = expression(bolditalic(paste("∆DOC"))), y = 61, x = 25, size = 12) 

lay <- rbind(c(1,1,2,2))

# a <- arrangeGrob(n, top = textGrob("A", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"), gp = gpar(col = "black", fontsize = 40, fontfamily = "sans", fontface = "bold")))
# 
# b <- arrangeGrob(doc, top = textGrob("B", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"), gp = gpar(col = "black", fontsize = 40, fontfamily =  "sans", fontface = "bold")))

combined_r.plot <- grid.arrange(n, doc, layout_matrix = lay )  
```

```{r include = FALSE}
# ggsave("f3.jpg", combined_r.plot, device = "jpg",  width = 16, height = 12, path = "~/Desktop/Export_MS/Submission2/") 
```

# Figure 4. ∆DOC, NCP, DOC:NCP Profiles

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 19, fig.align = "center", warning = FALSE}
f3a <-  profiles.df %>% 
  filter(Target_Z < 150) %>% 
  ggplot(aes(x = Target_Z, y = NCP_umol, group = Station)) +
   geom_segment(aes(y = min(NCP_umol), yend = max(NCP_umol), x = ave_chlmax, xend = ave_chlmax, group = Station),colour = "#4DAF4A", linetype = 3, size = 3 , alpha = 0.7) +
  geom_segment(aes(y = min(NCP_umol), yend = max(NCP_umol), x = ave_pmax, xend = ave_pmax, group = Station),colour = "#377EB8", linetype = 3, size = 3, alpha = 0.7 ) +
  geom_line(aes(colour = Season), size = 0.7) +
  geom_point(aes(fill = Season), size = 8, shape = 21, color = "black", stroke = 1, alpha = 0.7) + 
  labs(x = expression(italic(paste("Depth, m"))), y = expression(italic(paste("NCP, µmol C"," ", "L"^"-1"))), colour = "") +
  scale_x_reverse(breaks = pretty_breaks(), expand = c(0,0.1)) +
  coord_flip() +
  scale_y_continuous(expand = c(0,0)) +
  scale_colour_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  guides(colour = F) +
  guides(fill = F) +
  custom_theme2()  +
   annotate( geom = "text", label = expression(bolditalic(paste("CM"))), y = 15, x = 54.5, size = 12, color = "#4DAF4A") +
   annotate( geom = "text", label = expression(bolditalic(paste("PAM"))), y = 17, x = 15.5, size = 12, color = "#377EB8") 
 

f3b <-   profiles.df %>% 
  filter(Target_Z < 150) %>% 
  ggplot(aes(x = Target_Z, y = delta_DOC, group = Station)) +
  geom_segment(aes(y = min(delta_DOC), yend = max(delta_DOC), x = ave_chlmax, xend = ave_chlmax, group = Station), colour = "#4DAF4A", linetype = 3, size = 3, alpha = 0.7 ) +
  geom_segment(aes(y = min(delta_DOC), yend = max(delta_DOC), x = ave_pmax, xend = ave_pmax, group = Station), colour = "#377EB8", linetype = 3, size = 3, alpha = 0.7 ) +
  geom_line(aes(colour = Season), size = 0.7) +
  geom_point(aes(fill = Season), size = 8, shape = 21, color = "black", stroke = 1, alpha = 0.7) + 
  labs(x = expression(paste(italic(""))), y = expression(italic(paste("∆DOC, µmol C"," ", "L"^"-1"))), colour = "") +
  scale_x_reverse(breaks = pretty_breaks(), expand = c(0,0.1)) +
  coord_flip() +
  scale_y_continuous(expand = c(0,0)) +
  scale_colour_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  guides(colour = F) +
  guides(fill = F) +
  custom_theme2() 
   

f3c <- profiles.df %>% 
  filter(Target_Z < 150) %>% 
  ggplot(aes(x = Target_Z,  y = doc_ncp, group = Station)) +
  geom_segment(aes(y = min(doc_ncp), yend = max(doc_ncp), x = ave_chlmax, xend = ave_chlmax, group = Station),colour = "#4DAF4A", linetype = 3, size = 3, alpha = 0.7 ) +
  geom_segment(aes(y = min(doc_ncp), yend = max(doc_ncp), x = ave_pmax, xend = ave_pmax, group = Station),colour = "#377EB8", linetype = 3, size = 3, alpha = 0.7 ) + 
  geom_line(aes(colour = Season), size = 0.7) +
  geom_point(aes(fill = Season), size = 6, shape = 21, color = "black", stroke = 1, alpha = 0.7) + 
  labs(x = expression(italic(paste(""))), y = expression(italic(paste("∆DOC:NCP"))), colour = "") +
  scale_x_reverse(breaks = pretty_breaks(), expand = c(0,0)) +
  coord_flip() +
  scale_y_continuous(expand = c(0,0),) +
  scale_colour_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  guides(colour = F) +
  guides(fill = F) +
  custom_theme2() 
  

lay <- rbind(c(1,2,3))

# a <- arrangeGrob(f3a, top = textGrob("A", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"), gp = gpar(col = "black", fontsize = 40, fontfamily = "sans", fontface = "bold")))
# 
# b <- arrangeGrob(f3b, top = textGrob("B", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"), gp = gpar(col = "black", fontsize = 40, fontfamily = "sans", fontface = "bold")))
# 
# c <- arrangeGrob(f3c, top = textGrob("C", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"), gp = gpar(col = "black", fontsize = 40, fontfamily = "sans", fontface = "bold")))

combined_r.plot <- grid.arrange(f3a,f3b, f3c, layout_matrix = lay )  

```
```{r include = FALSE}
# ggsave("f4.jpg", combined_r.plot, device = "jpg",  width = 20, height = 8, path = "~/Desktop/Export_MS/Submission2/") 
```

# Figure 5. DOC:NCP Boxplots

```{r}
f4_data <- regression.means %>% 
  select(Season, doc_ncp_100) %>% 
  filter(!Season == "Early Spring") %>% 
  distinct()
f4_test <- t.test(doc_ncp_100 ~ Season, data = f4_data)
```

```{r echo = FALSE}
pander(f4_test)
```

```{r fig.align="center", fig.height=6, fig.width=7, echo = FALSE, message = FALSE, warning=FALSE}
f4.plot <- ggplot(f4_data,aes(Season, doc_ncp_100)) +
  geom_boxplot(outlier.shape = NA, notch = F, color = "black", alpha = 0.4) +
  geom_jitter(shape = 21, color = "black", alpha = 0.7, size = 6, stroke = 1, width = 0.25) +
  stat_summary(fun.y = mean, geom = "point", shape = 23, size = 4, fill = "white", stroke = 2) +
  annotate( geom = "text", label = "t = -2.50, df = 10, p = 0.03", x = "Late Spring", y = 0.38, size = 6) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.4)) +
  labs(y = expression(italic(paste("∆DOC:NCP"))), x = "") +
  scale_fill_manual(values = custom.colors) +
  guides(fill = F) +
  custom_theme2() 

f4.plot 
```

```{r include = FALSE}
# ggsave("f5.jpg", f4.plot, device = "jpg",  width = 7, height = 6, path = "~/Desktop/Export_MS/Submission2/") 
```

# Figure 6. DOC:NCP v NCP and Export v NCP

```{r, message = FALSE}
f5_data <- regression.means.aut %>% 
  select(Subregion,  doc_ncp_100, int_delta_DOC_100_maxmld,NCP_mol_100) %>% 
  distinct()

f5b <- lmodel2(int_delta_DOC_100_maxmld ~ NCP_mol_100, data = f5_data, nperm = 99)
```

```{r echo = FALSE}
f5b
```


```{r fig.align="center", fig.height=8, fig.width=16, echo = FALSE, message=FALSE, warning=FALSE}

f5a.plot  <- f5_data %>%  
  ggplot() +
  geom_point( aes(x = NCP_mol_100, y = doc_ncp_100, fill = Subregion), size = 8, shape = 21, alpha = 0.8, stroke=2) +
  labs(x = expression(italic(paste("NCP, mol C"," ", "m"^"-2"))), y = expression(italic(paste("∆DOC:NCP")))) +
  custom_theme2() +
  scale_fill_manual(values = c(custom.colors)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_y_continuous(breaks = pretty_breaks()) +
  guides(fill = F) 


f5b.plot  <- f5_data  %>%
  ggplot() +
  geom_abline(intercept = f5b$regression.results[3,2],
              slope = f5b$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( aes(x = NCP_mol_100, y = int_delta_DOC_100_maxmld, fill = Subregion),size = 8, shape = 21, alpha = 0.8, stroke = 2) +
  labs(x = expression(italic(paste("NCP, mol C"," ", "m"^"-2"))), y = expression(italic(paste("Annual DOC Export, mol C"," ", "m"^"-2")))) +
  custom_theme2() +
  scale_fill_manual(values = c(custom.colors)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_y_continuous(breaks = pretty_breaks()) +
  guides(fill = F) +
  annotate( geom = "text", label = expression(atop("y = 0.15x - 0.12", paste("r"^2,"= 0.77, p < 0.01"))), x = 5.5, y = 0.4, size = 7) 


lay <- rbind(c(1,2))

# a <- arrangeGrob(f5a.plot, top = textGrob("a", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"), gp = gpar(col = "black", fontsize = 40, fontfamily = "sans", fontface = "bold")))
# 
# b <- arrangeGrob(f5b.plot, top = textGrob("b", x = unit(0, "npc"), y   = unit(1, "npc"), just = c("left","top"),gp = gpar(col = "black", fontsize = 40, fontfamily = "sans", fontface = "bold")))

combined_r.plot <- grid.arrange(f5a.plot ,f5b.plot , layout_matrix = lay ) 
```
```{r include = FALSE}
# ggsave("f6.jpg", combined_r.plot, device = "jpg",  width = 16, height = 8, path = "~/Desktop/Export_MS/Submission2/") 
```


# Figure 7. Si:N

```{r}
f6_data <- regression.means.aut %>% 
  select(Subregion, si_n_100, ave_lat, doc_ncp_100) %>% 
  distinct()

f6a <- lm(si_n_100 ~ ave_lat, data = f6_data)
```

```{r echo = F}
summary(f6a)
```


```{r echo = F}
bptest(f6a)
```


```{r message = FALSE}
f6b <-  lmodel2(doc_ncp_100 ~ si_n_100, data = f6_data, nperm = 99)
```

```{r echo = FALSE}
f6b
```

```{r fig.align="center", fig.height=8, fig.width=18, echo = FALSE, message=FALSE, warning=FALSE}

int6a <- as.matrix(f6a$coefficients)

f6a.plot <- f6_data %>%  
  ggplot() +
  geom_abline(intercept = int6a[1,1],
              slope = int6a[2,1],colour = "black", linetype = 2, size = 1) + 
  geom_point( aes(x = ave_lat, y = si_n_100, fill = Subregion),size = 8, shape = 21, alpha = 0.8, stroke = 2) +
  labs(x = expression(italic(paste("Latitude, ˚N"))), y = expression(italic(paste("∆SiO"[4],":∆NO"[3])))) +
  custom_theme2() +
  scale_fill_manual(values = c(custom.colors)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_y_continuous(breaks = pretty_breaks()) +
  guides(fill = F)  +
  annotate( geom = "text", label = expression(atop(paste("y = 0.01x - 0.17, ", "r"^2,"= 0.77, p < 0.01;"), paste("Slope t-value = 2.00, p < 0.07; Breush-Pagan test p = 0.30"))), x = 48.1, y = 0.37, size = 6.5) 

f6b.plot <- f6_data %>%  
  ggplot() +
  geom_abline(intercept = f6b$regression.results[3,2],
              slope = f6b$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( aes(x = si_n_100, y = doc_ncp_100, fill = Subregion),size = 8, shape = 21, alpha = 0.8, stroke = 2) +
  labs(x = expression(italic(paste("∆SiO"[4],":∆NO"[3]))), y = expression(italic(paste("∆DOC:NCP")))) +
  custom_theme2() +
  scale_fill_manual(values = c(custom.colors)) +
  scale_y_continuous(breaks = pretty_breaks()) +
  scale_x_continuous(breaks = pretty_breaks()) +
  guides(fill = F) +
  annotate( geom = "text", label = expression(atop("y = -0.58x + 0.50", paste("r"^2,"= 0.63, p < 0.01"))), x = 0.65, y = 0.34, size = 7) 

lay <- rbind(c(1,2))

# a <- arrangeGrob(f6a.plot, top = textGrob("a", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"),gp = gpar(col = "black", fontsize = 40, fontfamily = "Times Roman")))
# 
# b <- arrangeGrob(f6b.plot, top = textGrob("b", x = unit(0, "npc"), y = unit(1, "npc"), just = c("left","top"),gp = gpar(col = "black", fontsize = 40, fontfamily = "Times Roman")))

combined_r.plot <- grid.arrange(f6a.plot, f6b.plot, layout_matrix = lay ) 
```

```{r include = FALSE}
# ggsave("f7.jpg", combined_r.plot, device = "jpg",  width = 18, height = 7, path = "~/Desktop/Export_MS/Submission2/") 
```

# Figure 8. ∆DOC:NCP v Pro


```{r message = FALSE}
f7_data <- regression.means %>% 
  select(Subregion, doc_ncp_cm, int_Pro_cm_vol, doc_ncp_phy, int_Pro_phy_vol) %>% 
  distinct()

f7a <- lmodel2(doc_ncp_cm ~ int_Pro_cm_vol, data = f7_data , nperm = 99)
```

```{r echo = FALSE}
f7a
```

```{r message = FALSE}
f7b <- lmodel2(doc_ncp_phy ~ int_Pro_phy_vol, data = f7_data, nperm = 99)
```

```{r echo = FALSE}
f7b
```

```{r fig.align="center", fig.height=10, fig.width=18, echo = FALSE, message=FALSE, warning=FALSE}
f7a.plot <- f7_data %>%  
  ggplot() +
  geom_abline(intercept = f7a$regression.results[3,2],
              slope = f7a$regression.results[3,3], colour = "black", linetype = 2, size = 1) +
  geom_point( aes(x = int_Pro_cm_vol, y = doc_ncp_cm, fill = Subregion),size = 8, shape = 21, alpha = 0.8, stroke = 2) +
  labs(x = expression(italic(paste("Prochlorococcus", ", cells L"^"-1"))), y = expression(italic(paste("∆DOC:NCP")))) +
  custom_theme2() +
  scale_fill_manual(values = c(custom.colors)) +
  scale_y_continuous(breaks = pretty_breaks(), limits = c(0.1,0.4)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  guides(fill = F) +
  ggtitle("Integrated to CM") +
  theme(plot.title = element_text(size = 30, face = "bold"),
        axis.text.x = element_text(angle = 90)) +
  annotate( geom = "text", label = expression(atop("y = 2.82e-09x + 0.13", paste("r"^2,"= 0.51, p = 0.01"))), x = 7*10^7, y = 0.11, size = 7) 

f7b.plot <- f7_data %>%  
  ggplot() +
  geom_abline(intercept = f7b$regression.results[3,2],
              slope = f7b$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( aes(x = int_Pro_phy_vol, y = doc_ncp_phy, fill = Subregion),size = 8, shape = 21, alpha = 0.8, stroke = 2) +
  labs(x = expression(italic(paste("Prochlorococcus", ", cells L"^"-1"))), y = expression(italic(paste("∆DOC:NCP")))) +
  custom_theme2() +
  scale_fill_manual(values = c(custom.colors)) +
  scale_y_continuous(breaks = pretty_breaks(), limits = c(0.1,0.4)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  guides(fill = F) +
  ggtitle("Integrated to PAM") +
    theme(plot.title = element_text(size = 30, face = "bold"),
        axis.text.x = element_text(angle = 90)) +
  annotate( geom = "text", label = expression(atop("y = 3.53e-09x + 0.12", paste("r"^2,"= 0.46, p = 0.04"))), x = 7*10^7, y = 0.11, size = 7)


lay <- rbind(c(1,2))

# a <- arrangeGrob(f7a.plot, top = textGrob("a", x = unit(0, "npc"), y   = unit(1, "npc"), just = c("left","top"), gp=gpar(col = "black", fontsize = 40, fontfamily = "Times Roman")))
# 
# b <- arrangeGrob(f7b.plot, top = textGrob("b", x = unit(0, "npc"), y   = unit(1, "npc"), just = c("left","top"),gp = gpar(col = "black", fontsize = 40, fontfamily = "Times Roman")))

combined_r.plot <- grid.arrange(f7a.plot,f7b.plot, layout_matrix = lay ) 
```

```{r include = FALSE}
# ggsave("f8.jpg", combined_r.plot, device = "jpg",  width = 16, height = 8, path = "~/Desktop/Export_MS/Submission2/") 
```

# Supplemental Figures. Profiles

See ProcessedExport.rMD document

```{r include = F}
#converting pdf images from ppt to jpg

# fig.pdf <- image_read_pdf("~/Desktop/Export_MS/Final_Figures/f8_conv.pdf")
# fig.jpg <- image_convert(fig.pdf, "jpeg")
# image_write(fig.jpg, path = "~/Desktop/Export_MS/Final_Figures/f8.jpg", format = "jpeg")


```

